```{r setup, include=F}
setwd('/net/store/nbp/projects/EEG/blind_spot/git_blind_spot_psychophy/scripts')
knitr::opts_chunk$set(echo=F,warning=F,message=F,cache=F,autodep=T,fig.width=12,fig.height=8)
knitr::opts_chunk$set(cache=F)
#knitr::opts_chunk$set(fig.path = "../cache/knitr/", dev='pdf') # corrected path and added dev
```

```{r Read Data}

#setwd('C:/Users/behinger/Dropbox/blindspot/bs_svn/analysis/r-analysis/stan_2015')
# 1. Read in the data
load('../data/behavioural/AllDataFrame_alsoBad.RDATA') #allDataFrame <- createAllDataFrame()

source('bs_ggplot_theme.R')
library(boot)
library(ggplot2)
library(plyr)
library(ggmcmc)
library(rstan)
rstan_options(auto_write = TRUE)
options(mc.cores = parallel::detectCores()-1)

#dat.raw = allDataFrame;
#dat = subset(dat.raw, with(dat.raw,subject!=26&subject!='M'&success == 1))
dat= subset(allDat,allDat$remove==F&allDat$success==1);
dat.orth = subset(dat,dat$stimPVisible == 2)
dat.uni  = subset(dat,dat$stimPVisible != 2)

dat.uni$subjectIndex = as.numeric(factor(dat.uni$subject))
dat.uni$controlTrial = as.factor(dat.uni$controlTrial)
source('bs_paper_main.r')

```


```{R generate Design Matrix & Labels,echo=T}
# 2. Make design matrix.
dat.uni$controlTrial = as.factor(dat.uni$controlTrial)
formula = ~1+stimLLoc*controlTrial + controlTrial*stimRLoc +oneBack
#formula = ~1+stimLLoc*controlTrial*stimRLoc +oneBack

X <- unname(model.matrix(formula, dat.uni))
X_fix = with(dat.uni,cbind(handedness,dominantEye,experiment=='Control',experiment=='Horizontal'))
```
```{r rename Parameters}

betaNames = colnames( model.matrix(formula, dat.uni))

betaNames[11:13] = c("stimRLoc:controlTrial1", "stimRLoc:controlTrial2", "stimRLoc:controlTrial3")
beta_fix_Names = c('handedness','dominantEye','ExperimentControl','ExperimentHorizontal')
label_dataframe = data.frame(Parameter=sprintf('beta.%i.',1:length(betaNames)),Label=betaNames)
label_dataframe = rbind(label_dataframe,data.frame(Parameter=sprintf('beta_fix.%i.',1:length(beta_fix_Names)),Label=beta_fix_Names))
attr(X,"assign") <- NULL
attr(X_fix,"assign") <- NULL
```

Because the sampling takes approx. 2.7h we load it
```{R Run Stan,echo=T}
# 4. Make Stan data.
stanDat <- within(list(),
                  {
                    N<-nrow(X)
                    P <- n_u <- n_w <- ncol(X)
                    P2 <- ncol(X_fix)
                    X <- Z_u <- Z_w <- X
                    X_fix <- X_fix
                    J <- length(levels(dat.uni$subject))
                    answer <- as.logical(dat.uni$answer)
                    subj <- as.integer(dat.uni$subject)
                  }
)
# 5. Fit the model.
#factorialFit <- stan(file="matrix_model.stan",data=stanDat,iter=2000, chains=6,cores = 6,open_progress = T)



load('../cache/stan/stan_with_between_22_09_2015.RData')

```

```{r Diagnostic Plots}

S = ggs(factorialFit,par_labels = label_dataframe,family = 'beta')
```
## Convergence Diagnostics

### Autocorrelation
```{r,echo=T} 
ggs_autocorrelation(S)
```
Autocorrelation seem to be OK.
### Potential Scale Reduction factor
```{r,echo=T}
ggs_Rhat(S)
```
All are below 1.1, we have indications that we converged on a useful solution

### Partial Density
```{r,echo=T,fig.height=14}
ggs_compare_partial(S)
```
The first 10% seem to be in the same range as the rest of the parameters for all chains, thus burnin/warmup was enough


## Posterior Densities
```{r,echo=T,fig.height=14}
ggs_density(S)+coord_cartesian(xlim=c(-1,1))
ggs_caterpillar(S)
```

## Contrasts of interest
In general, contrasts can be calculated by subtracting samples of the chains of factors of interest. One has to be careful because this quantity does not have a direct prior, and is susceptible to the borel-Kolmonogrov Paradox.

We fold over the two eyes/temporal fields. I.e. we take (left-right)/2 which takes the mean with one side inverted (the effect goes to the other side here).

To test whether BS is special, we take the differences of the BS effect and the now calculated location effects. We show 95% and 99% HDI
```{r Contrasts, echo=F}
extP = function(x){
  return(S[S$Parameter==x,'value'][[1]])
}
mcmccontrast = rbind(
  data.frame(Parameter='location outside',value= (extP('stimLLoc') - (extP('stimRLoc')))/2),
  data.frame(Parameter='location BS',value= ( ((extP('stimLLoc') + extP('stimLLoc:controlTrial1')) - (extP('stimRLoc') + extP('stimRLoc:controlTrial1'))))/2),
  data.frame(Parameter='location inside',value= ( ((extP('stimLLoc') + extP('stimLLoc:controlTrial2')) - (extP('stimRLoc') + extP('stimRLoc:controlTrial2'))))/2),
  data.frame(Parameter='location above',value= ( ((extP('stimLLoc') + extP('stimLLoc:controlTrial3')) - (extP('stimRLoc') + extP('stimRLoc:controlTrial3'))))/2),
  data.frame(Parameter='BS - outside',value = ((extP('stimLLoc:controlTrial1')) - extP('stimRLoc:controlTrial1'))/2),
  data.frame(Parameter='BS - inside',value  = ((extP('stimLLoc:controlTrial1') - extP('stimLLoc:controlTrial2')) - (extP('stimRLoc:controlTrial1') - extP('stimRLoc:controlTrial2')))/2),
  data.frame(Parameter='BS - above',value   = ((extP('stimLLoc:controlTrial1') - extP('stimLLoc:controlTrial3')) - (extP('stimRLoc:controlTrial1') - extP('stimRLoc:controlTrial3')))/2),
  data.frame(Parameter='outsi - insi',value = ((- extP('stimLLoc:controlTrial2')) - (extP('stimRLoc:controlTrial2')))/2),
  data.frame(Parameter='outsi - above',value= ((-extP('stimLLoc:controlTrial3')) - (-extP('stimRLoc:controlTrial3')))/2),
  data.frame(Parameter='insi - above',value = ((extP('stimLLoc:controlTrial2') - extP('stimLLoc:controlTrial3')) - (extP('stimRLoc:controlTrial2') - extP('stimRLoc:controlTrial3')))/2),
  data.frame(Parameter='BS - all',value     = ((extP('stimLLoc:controlTrial1') - (extP('stimLLoc:controlTrial2')+extP('stimLLoc:controlTrial3'))/3) - (extP('stimRLoc:controlTrial1') - (extP('stimRLoc:controlTrial2')+extP('stimRLoc:controlTrial3'))/3))/2))

estimates = ddply(mcmccontrast,.(Parameter),function(x){
  cbind(data.frame(median=-median(x$value)),
        t(quantile(-x$value,c(0.01,0.025,0.975,0.99))))
})
colnames(estimates) = c('Parameter','median','hdi0.01','hdi0.025','hdi0.975','hdi0.99')

logit<- function(p){ log(p / (1-p))}
invlogit <- function(x){exp(x)/(1+exp(x))}


estimatesProb = cbind(Parameter=estimates[,1],invlogit(estimates[,2:6])*100-50)

ggplot(estimatesProb,aes(x = Parameter, y = median,ymin = `hdi0.025`, ymax = `hdi0.975`), position=position_dodge(width=.9)) +
  geom_point(size = 4) +
  geom_errorbar(size = 0.75, width = 0.15, 
                alpha = 0.5,position=position_dodge(width=.9)) +
  labs(x = NULL, y = "Median Temporal Over Nasal Preference [%]") +
  geom_abline(intercept = 0, slope = 0) +  theme(axis.text.x = element_text(angle = 45, hjust = 1))

estimatesProbRound  = cbind(estimatesProb$Parameter,round(estimatesProb[,-1],2))
```
[BS loc] = (effect over all experiments:  m = `r estimatesProbRound$median[2]`% HDI_95:[`r estimatesProbRound$hdi0.05[2]`%,`r estimatesProbRound$hdi0.95[2]`%])

In hindsight unsurprisingly, we find a temporal bias for selecting the temporal stimulus inside (`r estimatesProbRound$median[2]`%) as well as above the blind spot (`r estimatesProbRound$median[4]`% HDI_95=[`r estimatesProbRound$hdi0.05[4]`%,`r estimatesProbRound$hdi0.95[4]`%]). The bias was stronger inside the blind spot (Diff:`r estimatesProbRound$median[7]`%, HDI_95=[`r estimatesProbRound$hdi0.05[7]`%,`r estimatesProbRound$hdi0.95[7]`%]). 


The blind spot location revealed the strongest effect (`r estimatesProbRound$median[2]`%), while the location outwards resulted in a small bias of `r estimatesProbRound$median[1]`% (HDI_95=[`r estimatesProbRound$hdi0.05[1]`%,`r estimatesProbRound$hdi0.95[1]`%]), whereas the one inwards, thus closest to the fixation cross, resulted in a non-significant bias of `r estimatesProbRound$median[3]`% (HDI_95=[`r estimatesProbRound$hdi0.05[3]`%,`r estimatesProbRound$hdi0.95[3]`%]). Both locations show a significant difference in bias to the blind spot location (inwards vs. BS: `r estimatesProbRound$median[6]`% (HDI_95=[`r estimatesProbRound$hdi0.05[6]`%,`r estimatesProbRound$hdi0.95[6]`%]),   outwards vs BS: `r estimatesProbRound$median[5]`% (HDI_95=[`r estimatesProbRound$hdi0.05[5]`%,`r estimatesProbRound$hdi0.95[5]`%]).


```{r}
#  datAgg = ddply(normalize_answer(get_prob_answer(dat.uni)),.(subject,controlTrial),
#                 summarise,(mean(prob[stimLLoc==0&stimRLoc==1])-mean(prob[stimLLoc==1&stimRLoc==0]))/2,.drop=T)
# colnames(datAgg)=c('subject','controlTrial','prob')
#  
#  
#  myMean = function(x,d){return(mean(x[d],trim=0.0))}
#  aggCI = ddply(datAgg,.(controlTrial),function(x){
#    ci = boot.ci(boot(x$prob,myMean,10000),type='bca')
#    return(cbind(`hdi0.025`=ci$bca[4],`hdi0.975`=ci$bca[5],median=ci$t0))
#  })
#  combinedDat = rbind(aggCI[,2:4]*100,estimatesProb[,c(4,5,2)])
#  
#  combinedDat$type = c(rep('raw',4),rep('model',7))
#  combinedDat$Parameter = c(rep(1:4,2),5:7)
#  
#  cbbPalette <- c("#000000", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#  
#  ggplot(combinedDat,aes(x = Parameter, y = median,color=type))+
#    geom_point(size = 4,position=position_dodge(width=.4))+
#    geom_errorbar(aes(ymin = `hdi0.025`, ymax = `hdi0.975`),size = 0.75, width = 0.15, 
#                  alpha = 0.9,position=position_dodge(width=.4)) +
#    geom_point(data=cbind(datAgg,type='raw'),position=position_jitterdodge(jitter.width=0.2,dodge.width=.2),alpha=0.3,aes(x=as.numeric(controlTrial),y=prob*100,fill=1))+
#    labs(x = NULL, y = "Temporal Over Nasal Preference [%]") +tBE()+
#    geom_abline(intercept = 0, slope = 0) +  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
#    scale_x_discrete(breaks = 1:7, labels=c("outward", "Blind Spot","Inward","Above","BS vs Out","BS vs In", "BS vs Ab"))+theme(axis.text.x = element_text(angle = 90, hjust = ))+scale_color_manual(values=cbbPalette)
```

```{r}
get_prob_answer = function(dat){ ddply(dat, c("stimLLoc", "stimRLoc", "controlTrial", "subject","stimPVisible","stimLCP","stimRCP"), summarise, answer=mean(answer))}

  cbbPalette <- c("#56B4E9","#009E73", "#D55E00" , "#0072B2", "#CC79A7")
library(ggstance)
  plotDat = get_prob_answer(subset(dat,dat$experiment=='EEG'))
  plotDat$grouping = with(plotDat,interaction(stimLCP,stimRCP,stimLLoc,stimRLoc,stimPVisible))
  plotDat$grouping = factor(plotDat$grouping,unique(plotDat$grouping))
  plotDat$grouping = factor(plotDat$grouping,levels(plotDat$grouping)[c(2,9,3,6,1,10,11,12,7,8,4,5)])
  ggplot(plotDat, aes(x = grouping,
                  y = answer, color=factor(2*stimRLoc+stimLLoc),
                  fill=factor(2*stimRLoc+stimLLoc)))+
    geom_jitter(alpha=.3,
                aes(color=factor(2*stimRLoc+stimLLoc)),
                position = position_jitterdodge(jitter.width = .05,jitter.height=0,dodge.width = .9)) +
    stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",position=position_dodge(width=.9))+
    #stat_summary(fun.data = "mean_cl_boot", geom = "point",size=4,position=position_dodge(width=.9),size=5)+
    scale_color_discrete(guide=F)+
    scale_fill_discrete(guide=F)+
    coord_cartesian(ylim = c(0, 1)) +
    scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1),labels = function(x)sprintf('%i%%:%i%%',100-x*100,x*100))+
    tBE(base_family = 'sans',base_size = 16)

ggsave(filename="../export/exp1.pdf",useDingbats=FALSE,width=5,height=4)
```

```{r plot with each experiment separated}

get_prob_correct = function(dat){ ddply(dat, c("stimLLoc", "stimRLoc", "controlTrial", "subject"), summarise, prob=mean(correct))}

plot_data = function(dat){
  cbbPalette <- c("#56B4E9","#009E73", "#D55E00" , "#0072B2", "#CC79A7")
  
  dat$BSeffect = with(dat,(stimRLoc != stimLLoc) & (controlTrial == 1))
  dat$tempoEffect = with(dat,stimRLoc != stimLLoc)
  ggplot(dat, aes(x = interaction(controlTrial,experiment,tempoEffect,BSeffect),
                  y = prob*100, color=interaction(stimRLoc,stimLLoc),
                  shape=experiment,
                  fill=factor(controlTrial)))+
    geom_point(alpha=.3,
                position = position_jitterdodge(jitter.width = .05,jitter.height=0,dodge.width = .5)) +
    stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",position=position_dodge(width=.5))+
    #stat_summary(fun.data = "mean_cl_boot", geom = "point",size=4,position=position_dodge(width=.9),size=5)+
    #scale_x_discrete(breaks = 0:3, labels=c("outward \n (O . . + . . O)", "Blind Spot \n (. O . + . O .)","Inward \n (. . O + O . .)","Above\n (. ° . + . ° .)")) +
    #labs(x =NULL, y = "Answer 'right' (normalized) [%]") +
    coord_cartesian(ylim = c(55, 105))  +tBE(base_family = 'sans',base_size = 16)
    #scale_color_manual(values=cbbPalette,
    #                   name = "", 
    #                   labels = c("Both Nasal","Left Temporal / Right Nasal ", "Right Temporal / Left Nasal", "Both Temporal") )
}

#plot_data(get_prob_correct(dat.orth))+labs(y='Inset correctly Identified [%]')+geom_abline(intercept = 50, slope = 0) +coord_cartesian(ylim=c(0,110))
x = get_prob_answer(dat.uni)
x$prob = x$answer
x$subject = factor(x$subject)
data_to_plot = normalize_answer(x)
data_to_plot$experiment = factor(dat.uni$experiment[match(data_to_plot$subject,dat.uni$subject)],levels=c("EEG","Control","Horizontal"),labels =c('Exp.1','Exp.2','Exp.3'))
#data_to_plot$experiment =order(data_to_plot$experiment,c(2,1,3))
plot_data(data_to_plot)+coord_cartesian(ylim = c(-55,55))+geom_abline(intercept = 0, slope = 0)+scale_y_continuous(breaks=c(-50,-25,0,25,50))


ggsave(filename="../export/normalized_data-splitExperiments.pdf",useDingbats=FALSE,width=6,height=3,scale=1.5)
```

```{r child='bs_stan_singleExperiment_analysis.Rmd',cache=F}
```


```{r oneBack}
show(round(summary(factorialFit)$summary["sigma_u[7]",],2))
```

```{r otherEffects}
estimates.other = ddply(S,.(Parameter),function(x){
  cbind(data.frame(median=-median(x$value)),
        t(quantile(-x$value,c(0.01,0.025,0.975,0.99))))
})
colnames(estimates.other) =  c('Parameter','median','hdi0.01','hdi0.025','hdi0.975','hdi0.99')
estimates.other.prob = cbind(estimates.other[,1],round(50-100*invlogit(estimates.other[,2:6]),2))

a = sprintf('%s: median = %.2f%% (hdi_95=[%.2f%%, %.2f%%]\n',estimates.other.prob$`estimates.other[, 1]`,estimates.other.prob$median,estimates.other.prob$hdi0.975,estimates.other.prob$hdi0.025)
cat(paste(a,collapse = ''))
```
