```{r setupChild, include=F}
knitr::opts_chunk$set(echo=F,warning=F,message=F,cache=T,fig.width=12,fig.height=8)
#setwd('/net/store/nbp/users/behinger/projects/blindspot/git/scripts')
```
```{r load data}
library(plyr)
library(ggmcmc)

source('revisions_1/bs_init.R') # loads data and sets paths and imports packages
source('revisions_1/bs_load_stan.R') # loads STAN data
source('./revisions_1/bs_stan_summarise_posterior_per_experiment.R') # Extract appropriate Contrasts and HDI


es = estimates.exp.prob = bs_stan_summarise_posterior_per_experiment(factorialFit.exp1,factorialFit.exp2,factorialFit.exp3,factorialFit.exp4a,factorialFit.exp4b, dat.exp1,dat.exp2,dat.exp3,dat.exp4a,dat.exp4b)
```
BS Loc effect only experiment 1:  m = `r es$median[1]`% HDI_95:[`r es$hdi0.025[1]`%,`r es$hdi0.975[1]`%])

We found a temporal bias for selecting the temporal stimulus inside (`r es$median[2]`%  HDI_95:[`r es$hdi0.025[2]`%,`r es$hdi0.975[2]`%]) as well as above the blind spot (`r es$median[3]`% HDI_95=[`r es$hdi0.025[3]`%,`r es$hdi0.975[3]`%]). The bias was stronger inside the blind spot (Diff:`r es$median[4]`%, HDI_95=[`r es$hdi0.025[4]`%,`r es$hdi0.975[4]`%]). 

 The blind spot location again revealed the strongest effect (`r es$median[6]`%  HDI_95:[`r es$hdi0.025[6]`%,`r es$hdi0.975[6]`%]), while the location outwards resulted in a  bias of `r es$median[5]`% (HDI_95=[`r es$hdi0.025[5]`%,`r es$hdi0.975[5]`%]), whereas the one inwards, thus closest to the fixation cross, resulted in a non-significant bias of `r es$median[7]`% (HDI_95=[`r es$hdi0.025[7]`%,`r es$hdi0.975[7]`%]). Both locations show a significant difference in bias to the blind spot location (outward vs. BS: `r es$median[8]`% (HDI_95=[`r es$hdi0.025[8]`%,`r es$hdi0.975[8]`%]),   inward vs BS: `r es$median[9]`% (HDI_95=[`r es$hdi0.025[9]`%,`r es$hdi0.975[9]`%]).

```{r}
# Make a nice table with the overal experiment results
es
outes = NULL

extractPerExperiment = function(es,target){
tmp = rep('',length(es[,1]))
ix  =es$Parameter.experiment ==target
tmp[ix] = sprintf('%.2f%% \t[%.2f%%,%.2f%%]',es$median[ix],es$hdi0.025[ix],es$hdi0.975[ix])

return(tmp)
}
outes =data.frame(Parameter=(es[,2]))
#estimatesProbRound these come from the parent knitr "bs_stan_matrix"

outes$`Experiment 1 (95% CI)` = extractPerExperiment(es,'EEG')
outes$`Experiment 2 (95% CI)` = extractPerExperiment(es,'Control')
outes$`Experiment 3 (95% CI)` = extractPerExperiment(es,'Horiz')
outes$`Experiment 4A (95% CI)` = extractPerExperiment(es,'InsetA')
outes$`Experiment 4B (95% CI)` = extractPerExperiment(es,'InsetB')
outesAll=data.frame(parameter=estimatesProbRound$`estimatesProb$Parameter`,`All experiments (95% CI)`= sprintf('%.2f%% \t[%.2f%%,%.2f%%]',estimatesProbRound$median,estimatesProbRound$hdi0.025,estimatesProbRound$hdi0.975))
knitr::kable(outes)
knitr::kable(outesAll)
```


```{r}
source('revisions_1/bs_aggregatedEffects.R')
aggCI = bs_aggregatedEffects(dat.uni)
# ES are the bayesian model fits
es2 = estimates.exp.prob
# We handcode the position for the plot and changethe experimental names
es2$Parameter = c(2,2,4,7,1,2,3,5,6,2,2,4,8)
es2$experiment = factor(es2$Parameter.experiment, levels=c("EEG","Control","Horiz",'InsetA','InsetB'),labels =c('Exp.1','Exp.2','Exp.3','Exp.4a','Exp.4b'))

colnames(aggCI)[1] = 'Parameter'
aggCI$experiment[10:13] = c('Exp.3','Exp.3','Exp.2','Exp.4b')
combinedDat=rbind.fill(cbind(es2,type="model"),aggCI)

cbbPalette <- c("#000000", "#E69F00","#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
#----

# All experiments ordereed in one plot
ggplot(combinedDat,aes(x = Parameter, y = median,shape=experiment,color=type))+
  geom_point(size = 4,position=position_dodge(width=1))+
  geom_errorbar(aes(ymin = `hdi0.025`, ymax = `hdi0.975`),size = 0.75, width = 0.15, 
                alpha = 0.9,position=position_dodge(width=1)) +
  geom_point(data=datAgg,
             position=position_jitterdodge(jitter.width=0.1,dodge.width = 1),
             alpha=0.3,
             aes(x=as.numeric(controlTrial),
                 y=prob,
                 group=experiment),shape=1)+
  labs(x = NULL, y = "Temporal Over Nasal Preference [%]") +tBE(base_family = 'sans',base_size = 16)+
  geom_abline(intercept = 0, slope = 0) +
  scale_x_discrete(breaks = 1:7, labels=c("Outward", "Blind Spot","Inward","Above","BS vs Outward","BS vs Inward", "BS vs Above"))+scale_color_manual(values=cbbPalette,guide=F)+scale_shape_discrete(guide=F)



ggsave(filename="../export/Figure5_allExperiments_combined.pdf",useDingbats=FALSE,width=11.5,height=5)


#All experiments but split up (faceted) by experiment
cbbPalette <- c( "#CC79A7","#000000", "#E69F00")

p1 = ggplot(combinedDat,aes(x = Parameter, y = median,color=type))+
  geom_point(data=datAgg,  # Data Points
             position=position_jitter(width=0.1),
             alpha=0.3,
             aes(x=as.numeric(controlTrial),
                 y=prob,
                 group=experiment))+
    
  geom_errorbar(aes(ymin = `hdi0.025`, ymax = `hdi0.975`),size = 0.75, width = 0.3,  #Errorbars
                alpha = 0.9,position=position_dodge(width=.9)) +
  geom_point(size = 4,position=position_dodge(width=.9),pch=21,fill='white')+  # Central Tendency
  xlab('')+ylab("Temporal Over Nasal Preference [%]")+
  tBE(base_family = 'sans',base_size = 16)+
  geom_abline(intercept = 0, slope = 0) +
  facet_grid(.~experiment)+
  scale_x_discrete(breaks = 1:7, labels=c("Outward", "Blind Spot","Inward","Above","BS vs Outward","BS vs Inward", "BS vs Above"))+
  scale_y_continuous(position='top')+
  scale_color_manual(values=cbbPalette,guide=F)+
  scale_shape_discrete(guide=F)+coord_flip()+
   theme(strip.background = element_blank(),
       strip.text.x = element_blank())+
  annotation_custom(grob = grid::textGrob("Nasal Stimulus selected",  gp=grid::gpar(fontSize=12)),               ymin = -40, ymax = 20, xmin = 10, xmax = 10)+
  annotation_custom(grob = grid::textGrob("Temporal Stimulus selected",gp=grid::gpar(fontSize=8),just='right'),  ymin = 65, ymax = 65, xmin = 10, xmax = 10)
  #annotation_custom(grob = grid::textGrob("Nasal2 Stimulus selected"),  xmin = -30, xmax = 20, ymin = -3,ymax = 3) 


gt <- ggplotGrob(p1)
gt$layout$clip[grep("panel",gt$layout$name)] <- "off"
gt$layout$clip[gt$layout$name=="panel"] <- "off"
grid::grid.draw(gt)




ggsave(filename="../export/2017-01-20_differences-splitByExperiment.pdf",useDingbats=FALSE,width=11.5,height=2.5,scale=1.7)
```