```{r setup, include=F}
knitr::opts_chunk$set(echo=T,warning=F,message=T,cache=F,fig.width=12,fig.height=8)
library(plyr)
```
```{r Read Data}
#load('../data/behavioural/AllDataFrame_alsoBad.RDATA')

source('revisions_1/bs_init.R')
# Redefine dat and dat.orth and remove only the single subjects
dat2 = subset(allDat,allDat$removeReason!='Single')
dat.orth = subset(dat2,dat2$success==1&dat2$stimPVisible==2)
dat.uni = subset(dat2,dat2$success==1&dat2$stimPVisible!=2)


perf.ortho = ddply(dat.orth,.(subject,stimRLoc,stimLLoc,experiment),summarise,perf=mean(correct))



```

```{r measures}


taskInverse =                   ddply(subset(perf.ortho,perf.ortho$experiment!='Inset4a'),.(subject),summarise,num = sum(perf<0.5))
taskInverse = rbind(taskInverse,ddply(subset(perf.ortho,perf.ortho$experiment=='Inset4a'),.(subject),summarise,num = sum(perf>0.5)))
taskInverse.vp = taskInverse$subject[taskInverse$num>2]

taskBad =               ddply(subset(perf.ortho,perf.ortho$experiment!='Inset4a'),.(subject),summarise,num = sum(perf<0.75))
taskBad = rbind(taskBad,ddply(subset(perf.ortho,perf.ortho$experiment=='Inset4a'),.(subject),summarise,num = sum(perf>0.25)))
# Get subjects, which have more than two conditions a performance lower than 75%, but are not task-inverters
taskBad.vp = taskBad$subject[taskBad$num>=2][!(taskBad$subject[taskBad$num>=2] %in% taskInverse.vp)]

Ntotal = 175#136

Net = 4
Ntechnical = 9

NsingleRemove = 56
NinverseTask =  length(taskInverse.vp)
NtaskBad = length(taskBad.vp)
Nperformance = NinverseTask+NtaskBad

Nexperiment = Ntechnical + Net

Nremaining = Ntotal - Ntechnical - Net - NtaskBad - NinverseTask - NsingleRemove
NdoubleButSingle = length(unique(allDat$subject[allDat$removeReason=='Single']))

if(Nremaining!=length(unique(allDat$subject[allDat$remove==F]))-24){warning('something does not add up!')} # minus 24, because the inset subjects are counted twice


```
Over all experiments `r Ntotal` subjects took part. We removed `r round(NsingleRemove/Ntotal*100)`% (n=`r NsingleRemove`) due to the screening experiments (see below). An additional `r round((Nperformance)/Ntotal*100)`% (n=`r Nperformance`) were removed due to low performance (n=`r NtaskBad`,<75% correct in half of the locations in the unique condition) or inversion of task (n=`r NinverseTask`). The experimental data was not recorded in `r round(Nexperiment/Ntotal*100)`% (n=`r Nexperiment`) due to eye tracking calibration problems (n=`r Net`) and other problems during data collection (n=`r Ntechnical`). The remaining `r Nremaining` were recorded in the following experiments: 
```{r subject measures}
datUse = subset(allDat,allDat$remove==F)
dAgg = ddply(datUse,.(subject,experiment),function(x)data.frame(age=x$age[1],sex=x$sex[1]=='F',dEye=x$dominantEye[1],hand=x$handedness[1]))

d = ddply(dAgg,.(experiment),summarise,lowA = min(age),higA = max(age),mA = mean(age),s=sum(sex),e=sum(dEye),h=sum(hand),n=length(unique(subject)))
d$mA = round(d$mA,1)
dTot = summarise(dAgg,lowA = min(age),higA = max(age),mA = mean(age),s=sum(sex),e=sum(dEye),h=sum(hand),n=length(unique(subject)))
```
For the first experiment we analyzed `r d[2,'n']` subjects (age `r d[2,'mA']` [lo:`r d[2,'lowA']` hi:`r d[2,'higA']`], `r d[2,'s']` female, `r d[2,'h']` right handed, `r d[2,'e']` right-eye dominant) with a subset of 15 taking part in the EEG study of Ehinger et al.. In the second experiment we recorded `r d[1,'n']` subjects (age `r d[1,'mA']` [lo:`r d[1,'lowA']` hi:`r d[1,'higA']`], `r d[1,'s']` female, `r d[1,'h']` right handed, `r d[1,'e']` right-eye dominant) and in the third, `r d[3,'n']` subjects (age `r d[3,'mA']` [lo:`r d[3,'lowA']` hi:`r d[3,'higA']`], `r d[3,'s']` female, `r d[3,'h']` right handed, `r d[3,'e']` right-eye dominant). All analysis are based on these `r Nremaining` participants.


Alternative formulation:  
For the first experiment we analyzed `r d[2,'n']`, in the second  `r d[1,'n']`  and in the third, `r d[3,'n']` subjects (age `r dTot['mA']` [lo:`r dTot['lowA']` hi:`r dTot['higA']`], `r dTot['s']` female, `r dTot['h']` right handed, `r dTot['e']` right-eye dominant). All analysis are based on these `r Nremaining` participants.



Data of n = `r NdoubleButSingle` (of `r NsingleRemove`) subjects who failed the screening are also available for analysis.

```{r Trials}
dat_tmp = dat
dat_tmp$subject = factor(gsub("Inset4a","Inset4b",as.character(dat_tmp$subject)))
dat_tmp$experiment = factor(gsub("Inset4a","Inset4b",as.character(dat_tmp$experiment)))

Ntrialsremaining = ddply(dat_tmp,.(subject,experiment),summarise,nT=length(trial))
trialsQuantile = ddply(Ntrialsremaining,.(experiment),function(x)round(quantile(x$nT,c(0.05,0.95)))) # the variation is minor.
trialsQuantile = round(quantile(Ntrialsremaining$nT,c(0.05,0.95)))

# ambiguous trials
round(mean(ddply(dat_tmp,.(subject,experiment),summarise,nT=length(trial[stimPVisible<2]))$nT))
# ambiguous per condition
myMean = function(x,d){
m = mean(x[d],trim=0.2)

return(m)
};




trialDiffNasaltemporal = (ddply(dat_tmp,.(subject,experiment),summarise,nT=length(trial[stimPVisible<2 & (answer==1 & stimRLoc == 1) | (answer ==0 &  stimLLoc == 1)]))$nT-
ddply(dat_tmp,.(subject,experiment),summarise,nT=length(trial[stimPVisible<2 & (answer==1 & stimRLoc == 0) | (answer ==0 &  stimLLoc == 0)]))$nT)
ci = boot.ci(boot(trialDiffNasaltemporal,myMean,10000),type='bca')
cbind(ci$bca[c(4,5)],m=ci$t0)

```

After cleaning trials for fixation deviation and blinks on average `r round(mean(Ntrialsremaining$nT),0) ` [90%-quantile:`r trialsQuantile[1]`, `r trialsQuantile[2]`] remained.
